Type Refinements for the Working Class

### 2015-11-13 paper.tex
say "global section" following Mac Lane / Moerdijk p.47

   Intuitively, the general judgment $\GenJ{\Omega}{\mathcal{J}}$ is evident
   when the family of judgments $\mathcal{J}$ shall forevermore have a section
   (i.e. for any substitution $\Member{\vec{E}}{\square\Omega}$,
   $\mathcal{J}(\vec{E})$ shall be evident). Recall that metavariables have
   \emph{valences} rather than sorts; as such, the general judgment allows us to
   quantify over terms of higher type.

>>>>

   Intuitively, the general judgment $\GenJ{\Omega}{\mathcal{J}}$ is evident
   when the family of judgments $\mathcal{J}$ shall forevermore have a global
   section (i.e. for any substitution $\Member{\vec{E}}{\square\Omega}$,
   $\mathcal{J}(\vec{E})$ shall be evident). Recall that metavariables have
   \emph{valences} rather than sorts; as such, the general judgment allows us
   to quantify over terms of higher type.
